Ordinal regression models made easy. A tutorial on parameter interpretation, data simulation, and power analysis.

### 2023-12-06 paper/paper-new.Rmd
update

```{r}
library(distributional)
library(ggdist)
library(cowplot)

@@

latent_plot <- lat |> 
  ggplot(aes(x = x, y = m, dist = dist)) +
  stat_halfeye(aes(fill = after_stat(factor(findInterval(y, ths))))) +
  ylim(c(-4, 6)) +
  geom_hline(yintercept = probs_to_th(probs)) +
  theme(legend.position = "none")

probs_plot <- get_probs(~x, 2, probs, lat) |> 
  pivot_longer(starts_with("y")) |> 
  ggplot(aes(y = factor(x), x = value, fill = name)) +
  geom_col(position = position_dodge())

>>>>

```{r}
library(distributional)
library(ggdist)
library(cowplot)
library(tidyverse)

@@

latent_plot <- lat |> 
  ggplot(aes(x = factor(x), y = m, dist = dist)) +
  stat_halfeye(aes(fill = after_stat(factor(findInterval(y, ths))))) +
  ylim(c(-4, 6)) +
  geom_hline(yintercept = probs_to_th(probs)) +
  theme(legend.position = "none") +
  xlab("X")

probs_plot <- get_probs(~x, 2, probs, lat, append = TRUE) |> 
  pivot_longer(starts_with("y")) |> 
  ggplot(aes(x = factor(x), y = value, fill = name)) +
  geom_col(position = position_dodge()) +
  xlab("X")
